---
title: "Cabbages"
author: "Shaun Ikeuchi"
date: "1/31/24"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
We want to predict VitC based on cultivation method. 
VitC is numerical. Cult is a categorical, so we use the numerical~categorical helper file.
 
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(VitC~Cult,data=veggy)
```
 
The box plot shows that c52 cultivation has a higher vitaminC level than c39 cultivation.
 
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
 
This table shows that the mean number vitaminC levels in c52 (64.4) is greater than vitaminC levels in c39 (51.5). 

 
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult,data=veggy)
```
  
Since the p-value is 0.00000003405 which is less than 0.05, we reject the null hypothesis. 
 
# Discussion and Conclusion
 
The average number of vitaminC in C52 is statistically significant compared to the average number of vitaminC in c39, thus we reject the null hypothesis. First of all, the box plot displays a clear distinction between c52 and c39 cultivation methods. In addition, the means are different by 12.9 vitaminC. Futhermore, since the p-value is less than 0.05, we can conclude c52 cultivation allows for more vitaminC levels. 
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
